---
title: "Earth Hologenome Initiative | Gaun et al. 2025"
subtitle: "The Earth Hologenome Initiative: Data Release 1"
author:
  - Nanna Gaun, Raphael Eisenhofer, Carlotta Pietroni, Garazi Martin-Bideguren, Jonas Lauritsen, Ostaizka Aizpurua, Joana Fernandes, Eduardo Ferreira, Fabien Aubret, Tom Sarraude, Constant Perry, Lucas Wauters, Claudia Romeo,, Martina Spada, Claudia Tranquillo, Alex O Sutton, Michael Griesser, Miya Warrington, Guillem Pérez i de Lanuza, Javier Abalos, Prem Aguilar, Ferrán de la Cruz, Javier Juste, Pedro Alonso, Jim Groombridge, Rebecca Louch, Kevin Ruhomaun, Sion Henshaw, Carlos Cabido, Ion Garin Barrio, Emina Šunje, Peter Hosner, Tobias Uller, Nathalie Feiner, Antton Alberdi^[University of Copenhagen, antton.alberdi@sund.ku.dk]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
url: https://earthhologenome.github.io/EHI_data_release_1
description: |
  Summary statistics of the first EHI data release.
link-citations: yes
github-repo: earthhologenome/EHI_data_release_1
---

```{r knitr_opts, echo=FALSE}
knitr::opts_chunk$set(
    class.source = "script-source",
    class.output = "script-output",
    comment = NA)
```

# Introduction

This webbook contains all the code used for the comparative study on the generation of metagenomic data from faeces of various species using three extraction methods.

## Accession numbers

The ENA accession numbers can be found in the sample and raw data metadata tables stored in the Gihub repository:

> https://github.com/earthhologenome/EHI_data_release_1/tree/main/data

## Prepare the R environment

### Environment

To reproduce all the analyses locally, clone this repository in your computer using:

```
RStudio > New Project > Version Control > Git
```

And indicating the following git repository:

> https://github.com/earthhologenome/EHI_data_release_1.git

Once the R project has been created, follow the instructions and code chunks shown in this webbook.

### Libraries

The following R packages are required for the data analysis.

```{r load_libraries, warning=FALSE, comments="", message=FALSE}
# Base
library(R.utils)
library(tidyverse)
library(knitr)
library(tidyverse)
library(devtools)
library(tinytable)
library(rairtable)
library(phyloseq)
library(ggtree)
library(ape)
library(ggnewscale)
library(ggtreeExtra)
library(gridExtra)
library(ggh4x)
library(phytools)
```
